Nanophotonic Computational Design

### 2013-03-03 paper/paper.tex
Working on paper.

\section{Method}
% Problem statement 
In order to produce designs which utilize the full parameter space,
    and are based solely on the user's performance specification,
    we formulate the design problem in the following way:
\begin{subequations}\begin{align}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align} \label{problem}\end{subequations}

The explanation for the various terms in \eqref{problem} follows:
\begin{enumerate}
\item 
    $A_i(z)x_i - b_i$ is the \emph{physics residual} for the $i$th mode.
    That is to say, $A_i(z)x_i - b_i$ represents the underlying physics
        of the problem; namely, the electromagnetic wave equation
        \mbox{$(\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
            +i \omega_i J_i $}.

@@

\item
    The (field) design objective consist of 
        the constraint $\alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}$.
    Physically, this constraint describes 
        the performance specification of the device 
        via a series of field overlap integrals 
        at various output ports of the device.
    Specifically, the $c_{ij}\T x_i$ terms represents an overlap integral between
        the E-field of the $i$th mode ($x_i$)
        with an E-field of the user's choice ($c_{ij}$),
        where the additional subscript $j$ allows the user
        to include multiple such fields.

    The amplitude of the overlap integral is then forced

\end{enumerate}
% how we solved it
% Maxwell

>>>>

\section{Problem formulation}
% Problem statement 
In order to produce designs which utilize the full parameter space,
    and are based solely on the user's performance specification,
    we formulate the design problem in the following way:
\begin{subequations}\begin{align}
    \minimize & \sum_i^M \|A_i(z)x_i - b_i\|^2 \\
    \subto & \alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}, \quad
        \text{for $i = 1, \ldots, M$ and $j = 1, \ldots, N_i$} \\
        &   z_\text{min} \le z \le z_\text{max}
\end{align} \label{problem}\end{subequations}

The explanation for the various terms in \eq{problem} follows:
\begin{enumerate}
\item 
    $A_i(z)x_i - b_i$ is the \emph{physics residual} for the $i$th mode.
    That is to say, $A_i(z)x_i - b_i$ represents the underlying physics
        of the problem; namely, the electromagnetic wave equation
        \mbox{$(\nabla\times\mu_0^{-1}\nabla\times - \omega_i^2 \epsilon) E_i 
            +i \omega_i J_i $}.

@@

\item
    The (field) design objective consist of 
        the constraint $\alpha_{ij} \le |c_{ij}\T x_i| \le \beta_{ij}$.
    Physically, this constraint describes 
        the performance specification of the device 
        via a series of field overlap integrals 
        at various output ports of the device.
    Specifically, the $c_{ij}\T x_i$ terms represents an overlap integral between
        the E-field of the $i$th mode ($x_i$)
        with an E-field of the user's choice ($c_{ij}$),
        where the additional subscript $j$ allows the user
        to include multiple such fields.
    The amplitude of the overlap integral is then forced to reside between
        $\alpha_{ij}$ and $\beta_{ij}$.

    This mechanism allows the user to express 
        the desired performance of the device
        as a combination of field amplitudes in various output field patterns.
    These outputs would be in response to a predefined input excitation,
        which is determined by the current excitation $b_i$ ($-i\omega_i J_i$)
        in the physics residual of each mode.

    As an example of a design objective for some mode 1 
        a user might choose to have the majority of the output power
        reside in some output pattern 1,
        while ensuring that only a small amount of power 
        be transferred to some output pattern 2.
    In this case the user would use 
        $0.9 \le |c_{11}\T x_1| \le 1.0$ for the former.
        and then $0.0 \le |c_{12}\T x_1| \le 0.01$ for the latter;
        where $c_{11}$ and $c_{12}$ are representative of 
        output patterns 1 and 2 respectively.

    Finally, we note again that the design objective in our formulation
        is actually a hard constraint.
    This means that it is \emph{always satisfied}, 
        even to the extent of allowing for an unphysical field 
        (since the physics residual will not be exactly 0).
    It is for this reason that we call such a formulation ``objective-first''.

\item 
    The final term in \eq{problem}, $z_\text{min} \le z \le z_\text{max}$,
        is the structure design objective.
    It is used as a relaxation of the binary constraint,
        $z \in {z_\text{min}, z_\text{max}}$,
        which would ensure that the final design be composed 
        of two discrete materials.
\end{enumerate}

\section{Method of solution}
We employed the alternating directions method of multipliers (ADMM) algorithm % Ref!
    in order to solve \eq{problem}.
ADMM, at its core, solves \eq{problem} by iteratively solving for 
    $x_i$, $z$, and a dual variable $u_i$.
